A Tutorial on Tailored Simulation-Based Sample Size Planning for Experimental Designs with Generalized Linear Mixed Models

### 2024-07-01 manuscript.qmd
fix table headers

```{r}
#| tbl-cap: Table 1: Overview of software packages for power analysis for (generalized) linear mixed models in R.
#| apa-note: GUI available = whether a graphical user interface is provided (usually a Shiny app that is available online or can be downloaded to run locally), GLMM support = whether power analysis can be performed for generalized linear mixed model (otherwise only linear mixed models are supported), Design limitations = whether only a limited selection of study designs can be specified (otherwise arbitrary designs within the model class are supported).  
#| echo: false
#| message: false
# label: tbl-rpackages # There is currently a bug in apaquarto that prevents referencing for multipage tables (https://github.com/wjschne/apaquarto/issues/71)

@@

```{r}
#| tbl-cap: Table 2: Assumed probabilities that an average subject solves an average item in each experimental condition.
#| apa-note: Implied equations are derived based on the model equations and setting all random intercept terms to 0.
#| echo: false
probtable <- data.frame(
  col1 = 
    c("no advice, student", "no advice, expert", "incorrect advice, student", 
      "incorrect advice, expert", "correct advice, student", "correct advice, expert"),
  col2 =
    c("0.70", "0.90", "0.40", "0.85", "0.90", "0.95"),
  col3 = 
    c("$logit(0.70) = \\beta_0$",
      "$logit(0.90) = \\beta_0 + \\beta_e$", 
      "$logit(0.40) = \\beta_0 + \\beta_a$",
      "$logit(0.85) = \\beta_0 + \\beta_e + \\beta_{a} + \\beta_{ea}$",
      "$logit(0.90) = \\beta_0 + \\beta_a + \\beta_c$",
      "$logit(0.95) = \\beta_0 + \\beta_e + \\beta_a + \\beta_c + \\beta_{ea} + \\beta_{ec}$"))
knitr::kable(probtable, col.names = c("Experimental condition",
    "$P(Y=1 \\mid \\mathbf{X=x}, \\mathbf{U} = \\mathbf{0})$",
    "Implied equation"), escape = FALSE)
```

>>>>

```{r}
#| tbl-cap: Table 1. Overview of software packages for power analysis for (generalized) linear mixed models in R.
#| apa-note: GUI available = whether a graphical user interface is provided (usually a Shiny app that is available online or can be downloaded to run locally), GLMM support = whether power analysis can be performed for generalized linear mixed model (otherwise only linear mixed models are supported), Design limitations = whether only a limited selection of study designs can be specified (otherwise arbitrary designs within the model class are supported).  
#| echo: false
#| message: false
# label: tbl-rpackages # There is currently a bug in apaquarto that prevents referencing for multipage tables (https://github.com/wjschne/apaquarto/issues/71)

@@

```{r}
#| tbl-cap: Table 2. Assumed probabilities that an average subject solves an average item in each experimental condition.
#| apa-note: Implied equations are derived based on the model equations and setting all random intercept terms to 0.
#| echo: false
probtable <- data.frame(
  col1 = 
    c("no advice, student", "no advice, expert", "incorrect advice, student", 
      "incorrect advice, expert", "correct advice, student", "correct advice, expert"),
  col2 =
    c("0.70", "0.90", "0.40", "0.85", "0.90", "0.95"),
  col3 = 
    c("$logit(0.70) = \\beta_0$",
      "$logit(0.90) = \\beta_0 + \\beta_e$", 
      "$logit(0.40) = \\beta_0 + \\beta_a$",
      "$logit(0.85) = \\beta_0 + \\beta_e + \\beta_{a} + \\beta_{ea}$",
      "$logit(0.90) = \\beta_0 + \\beta_a + \\beta_c$",
      "$logit(0.95) = \\beta_0 + \\beta_e + \\beta_a + \\beta_c + \\beta_{ea} + \\beta_{ec}$"))
knitr::kable(probtable, col.names = c("Experimental condition",
    "$P(Y=1 \\mid \\mathbf{X=x}, \\mathbf{U} = \\mathbf{0})$",
    "Implied equation"), escape = FALSE)
```
